External validation

### 2021-01-19 diagnostics/README.Rmd
m

-   `P_Sex` and `P_ASA` should be self-explanatory
-   `P_BMI` is a broader categorization based on BMI and the [WHO classification] (<https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi>) where overweight = "pre-obesity"  
-   `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories.

>>>>

-   `P_Sex` and `P_ASA` should be self-explanatory
-   `P_BMI` is a broader categorization based on BMI and the [WHO classification] (<https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi>) where overweight = "pre-obesity"\
-   `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories.
